%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
	
	
	
	%---------------------------------------------------------
	\cventry
	{Data Analyst} % Job title
	{Texas Children's Hospital} % Organization
	{Houston, Tx} % Location
	{May. 2017 - PRESENT} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Collaborated with LIS and clinic management to mine data from a blood bank database system to create reports and drive initiatives to reduce waste.}
			\item {Reduced employee onboarding time by creating laboratory software training videos and interactive quizzes with Adobe Captive.}
			\item {Developed an application to convert Epic patient demographic report into a list of medical record bar codes, resulting in reduced staff workload and increased accuracy of patient-specific labeling.}
		\end{cvitems}
	}
	
	
	%---------------------------------------------------------
	\cventry
	{Laboratory Technician} % Job title
	{Texas Children's Hospital} % Organization
	{Houston, Tx} % Location
	{May. 2008 - May 2017} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Analyzed reports from Epic and Crystal Reports to plan daily operations and identify areas for improvement in both care and quality.}
			\item {Involved in daily interaction with physicians and nurses regarding the order for blood products, discrepancies and transfusion history
				on blood banking  transfusion management software HCLL.}
			\item {Process specimens and perform quality control testing.}
		\end{cvitems}
	}
	%---------------------------------------------------------
\end{cventries}
